Growing up with Nell: A Narrative Interface for Literacy

### 2012-03-11 paper.tex
Fix broken caption.

<category>
 <pattern>NORTH</pattern>
 <template>
  <javascript>FireEvent(Chat, "North")</javascript>
 </template>
</category>
</aiml>
\end{verbatim}
\caption{An AIML fragment which recognizes the commands ``N'',
  ``North'', and ``Go North''. The \verb|<srai>| tag invokes the
  recognizer recursively.}\label{fig:aiml}
\end{figure}
% show fragment
Each story module can include AIML fragments extending the
conversational capabilities of Nell's agents.  Figure~\ref{fig:aiml}
illustrates how this can be used to implement a traditional
text adventure interaction for a particular story module.
The child can write instructions such as, ``go north,'' ``go
east,'' or ``open door'' for the agent.  These trigger events
handled by the story module to move the agent through the
adventure---for example, by causing the activity to draw a
new location, causing the agent to describe it, and shifting the
AIML topic to enable vocabulary suitable for the new location.

>>>>

<category>
 <pattern>NORTH</pattern>
 <template>
  <javascript>FireEvent(Chat, "North")</javascript>
 </template>
</category>
</aiml>
\end{verbatim}
\caption{An AIML fragment which recognizes the commands \texttt{N},
  \texttt{North}, and \texttt{Go North}. The \texttt{<srai>} tag invokes the
  recognizer recursively.}\label{fig:aiml}
\end{figure}
% show fragment
Each story module can include AIML fragments extending the
conversational capabilities of Nell's agents.  Figure~\ref{fig:aiml}
illustrates how this can be used to implement a traditional
text adventure interaction for a particular story module.
The child can write instructions such as, ``go north,'' ``go
east,'' or ``open door'' for the agent.  These trigger events
handled by the story module to move the agent through the
adventure---for example, by causing the activity to draw a
new location, causing the agent to describe it, and shifting the
AIML topic to enable vocabulary suitable for the new location.
